---
title: "Wikileaks Twitter DM"
author: '@_colinfay'
date: "`r Sys.Date()`"
navlink: "[Wikileaks Twitter DM](https://colinfay.me/wikileaksdm)"
og:
  type: "article"
  title: "Wikileaks Twitter DM"
footer:
  - content: '<a href="https://colinfay.me">colinfay.me</a> • <a href="https://twitter.com/_ColinFay">@_colinfay</a><br/>'
output: markdowntemplates::skeleton
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(DT) 
dt <- partial(datatable, 
                     extensions = 'Buttons', 
                     options=list(scrollX=TRUE, dom = 'Bfrtip', buttons = c('copy', 'csv')))
```

<style>
h4 {
  text-align: center;
  font-size: 1.5em;
}
.dataTables_wrapper{
  padding-bottom: 30px ;
}
</style>

## About

On the 29th of July 2018, Emma Best published on her website the copy of 11k+ wikileaks Twitter DM : <https://emma.best/2018/07/29/11000-messages-from-private-wikileaks-chat-released/>

Here is a data extraction and wrangling of this corpus, to make it easily searchable, extractable and sharable. 

## The datasets: 

### List of all tweets

A dataset with 3 columns: 

+ text: extracted text 
+ date: date of the tweet
+ user: user who sent the tweet

#### Get the csv: [wikileaks_dm.csv](wikileaks_dm.csv)

```{r}
read_csv("wikileaks_dm.csv") %>% 
  dt()
```

### DMS by year 

#### 2015

#### [2015.csv](2015.csv)

```{r}
read_csv("2015.csv") %>% 
  dt()
```

#### 2016

#### [2016.csv](2016.csv)

```{r}
read_csv("2016.csv") %>% 
  dt()
```

#### 2017

#### [2017.csv](2017.csv)

```{r}
read_csv("2017.csv") %>% 
  dt()
```

### Count of user interactions

#### Get the csv: [user_count.csv](user_count.csv)

```{r}
read_csv("user_count.csv") %>% 
  dt()
```

### DMs by users

#### [user_Bean.csv](user_Bean.csv)
#### [user_Cabledrum.csv](user_Cabledrum.csv)
#### [user_DMConversationEntry.csv](user_DMConversationEntry.csv)
#### [user_Emmy.B.csv](user_Emmy.B.csv)
#### [user_LibertarianLibrarian.csv](user_LibertarianLibrarian.csv)
#### [user_M.csv](user_M.csv)
#### [user_Matt.Watt.csv](user_Matt.Watt.csv)
#### [user_noll.csv](user_noll.csv)
#### [user_SAWC.Sydney.csv](user_SAWC.Sydney.csv)
#### [user_voidiss.csv](user_voidiss.csv)
#### [user_WikiLeaks.Press.csv](user_WikiLeaks.Press.csv)
#### [user_WikiLeaks.Task.Force.csv](user_WikiLeaks.Task.Force.csv)
#### [user_WikiLeaks.csv](user_WikiLeaks.csv)
#### [user_WISE.Up.Action.csv](user_WISE.Up.Action.csv)
#### [user_WISE.Up.Wales.csv](user_WISE.Up.Wales.csv)


### Count of daily tweets

#### Get the csv: [daily.csv](daily.csv)

```{r}
read_csv("daily.csv") %>%
  dt()
```

### Mentions

Tweets that contains a mention to a Twitter account: 

#### Get the csv: [mentions.csv](mentions.csv)

```{r}
read_csv("mentions.csv") %>% 
  dt()
```

Count of the mentions:

#### Get the csv: [mentions_count.csv](mentions_count.csv)

```{r}
read_csv("mentions_count.csv") %>% 
  dt()
```

### Urls

Extracted links, (starting with `http`)

#### Get the csv: [urls.csv](urls.csv)

```{r}
read_csv("urls.csv") %>% 
  dt()
```

## Methodology 

Everything has been done in R. 

Methodology is described in [methodo](methodo.html)
