---
title: "Wikileaks Twitter DM - Mentions, urls"
author: '@_colinfay'
date: "`r Sys.Date()`"
fig_width: 10
fig_height: 4 
navlink: "[Wikileaks Twitter DM](https://colinfay.me/wikileaksdm)"
og:
  type: "article"
  title: "Wikileaks Twitter DM"
footer:
  - content: '<a href="https://colinfay.me">colinfay.me</a> • <a href="https://twitter.com/_ColinFay">@_colinfay</a><br/>'
output: markdowntemplates::skeleton
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("funs.R")
```

`r shiny::includeMarkdown("intro.Rmd")`

## Data format

+ Every csv is encoded in UTF8
+ You can find these csv in JSON format on the [GitHub repo](https://github.com/ColinFay/wikileaksdm)

## Browse through the content

+ [Home](index.html) has the full dataset, to search and download
+ [Timeline](timeline.html) has a series of time-related content: notably DMs by years, and daily count of DMs
+ [Users](users.html) holds the dataset for each users 
+ [mentions_urls](mentions_urls.html) holds the extracted mentions and urls
+ [text_mining](text_mining.html) contains a series of text-frequency based analysis (mainly most frequent words).

## Mentions

DMs that contain a mention to a Twitter account. 

A dataset with 4 columns 

+ mention: the mentioned account
+ text: extracted text 
+ date: the date
+ user: user who sent the dm

#### `r fa("download")` [mentions.csv](mentions.csv)

```{r}
read_csv("mentions.csv") %>% 
  dt()
```

### Count of the mentions:

A dataset with 2 columns 

+ mention: the mention
+ n: number of DMs 

#### `r fa("download")` [mentions_count.csv](mentions_count.csv)

```{r}
read_csv("mentions_count.csv") %>% 
  dt()
```

## Urls

Extracted links, (starting with `http`). 

A dataset with 4 columns 

+ url: the found url
+ text: extracted text 
+ date: the date
+ user: user who sent the dm

#### `r fa("download")` [urls.csv](urls.csv)

```{r}
read_csv("urls.csv") %>% 
  dt()
```

`r shiny::includeMarkdown("outro.Rmd")`