---
title: "Wikileaks Twitter DM - Methodo"
author: '@_colinfay'
date: "`r Sys.Date()`"
navlink: "[Wikileaks Twitter DM](https://colinfay.me/wikileaksdm)"
og:
  type: "article"
  title: "Wikileaks Twitter DM"
footer:
  - content: '<a href="https://colinfay.me">colinfay.me</a> • <a href="https://twitter.com/_ColinFay">@_colinfay</a><br/>'
output: 
  markdowntemplates::skeleton
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
source("funs.R")
```

`r shiny::includeMarkdown("intro.Rmd")`

## Raw to csv

### Downloading 

Made once, saved in [raw.txt](raw.txt). 

```{r message = FALSE, eval = FALSE}
library(tidyverse)
library(rvest)
doc <- read_html("https://emma.best/2018/07/29/11000-messages-from-private-wikileaks-chat-released/")
doc <- doc %>% 
  # Getting the p
  html_nodes("p") %>%
  html_text()

doc <- doc[! nchar(doc)  == 0]
# Element 1 to 9 are the content of the blogpost, not the content of the conversation. Removing it:

doc <- doc[10:length(doc)]
write(doc, "raw.txt")
```

### Getting data as a table

```{r}
library(tidyverse)
res_raw <- read.delim("raw.txt", sep = "\n", header = FALSE) %>% 
  as.tibble() %>% 
  rename(value = V1)
```

In order to tidy the format, add <DMConversationEntry> as author when the text is a `DMConversationEntry`

```{r}
res <- res_raw %>% 
  mutate(value = str_replace_all(value, 
                                 "\\[DMConversationEntry\\]",
                                 "<DMConversationEntry>")) 
```

Removed, the last of the corpus: 

+ "[LatestTweetID] 931704226425856001", line 22751 of the original document

```{r}
res <- filter(res, ! str_detect(value, "931704226425856001"))
```


When a line `n` doesn't start with a date (middle of a DM), paste the content at the end of the line n-1.

Example with lines 93 & 94:

|  value|
|--:|
|  "[2015-05-02 14:12:27] <WISE Up Wales> OK, thanks H. Security issues were about who was on the list then?"|
|  "Never quite know who you’re dealing with online I guess. I don’t, anyway!"|

94 is paste at the end of 93 and removed. 

```{r}
for (i in nrow(res):1){
  if (!grepl(pattern = "\\[.{4}-.{2}-.{2} .{2}:.{2}:.{2}\\]|DMConversationEntry", res[i,])){
    res[i-1,] <- paste(res[i-1,], res[i,])
  }
}
# Remove column with no date
res <- res %>% 
  mutate(has_date = str_detect(value, pattern = "\\[.{4}-.{2}-.{2} .{2}:.{2}:.{2}\\]|DMConversationEntry")) %>%
  filter(has_date) %>%
  select(-has_date)
```

### Extract key elements 

```{r}
res <- res %>%
  extract(value,"user", regex = "<([a-zA-Z0-9 ]*)>", remove = FALSE) %>%
  extract(value,"date", regex = "\\[(.{4}-.{2}-.{2} .{2}:.{2}:.{2})\\] .*", remove = FALSE) %>%
  extract(value, "text", regex = "<[a-zA-Z0-9 ]*> (.*)", remove = FALSE) %>%
  select(-value)
```

When date is missing, it's because it's a `DMConversationEntry`. 

```{r}
res %>% 
  filter(user == "DMConversationEntry") %>%
  summarize(nas = sum(is.na(date)), 
            nrow = n())
```

We fill this with the directly preceeding date: 

```{r}
res <- fill(res, date)
```

### Save

#### Global

```{r}
write_csv(res, "wikileaks_dm.csv")
```

#### Year

```{r}
range(res$date)
```

```{r}
walk(2015:2017, 
    ~ filter(res, lubridate::year(date) == .x) %>%
    write_csv(glue::glue("{.x}.csv"))
    )
```

#### User

```{r}
walk(unique(res$user), 
    ~ filter(res, user == .x) %>%
    write_csv(glue::glue("user_{make.names(.x)}.csv"))
    )
```

## Counting users participation

```{r}
res %>%
  count(user, sort = TRUE) %>%
  write_csv("user_count.csv")
```

## Counting activity by days

```{r}
res %>%
  mutate(date = lubridate::ymd_hms(date), 
         date = lubridate::date(date)) %>% 
  count(date) %>%
  write_csv("daily.csv")
```

## Adding extra info

```{r}
mentions <- res %>% 
  mutate(mention = str_extract_all(text, "@[a-zA-Z0-9_]+")) %>%
  unnest(mention) %>% 
  select(mention, everything())
write_csv(mentions, "mentions.csv")

mentions %>%
  count(mention, sort = TRUE) %>%
  write_csv("mentions_count.csv")
```

```{r}
urls <- res %>% 
  mutate(url = str_extract_all(text, "http.+")) %>%
  unnest() %>% 
  select(url, everything())
write_csv(urls, "urls.csv")
```

## Adding JSON format

```{r}
list.files(pattern = "csv") %>%
  walk(function(x) {
    o <- read_csv(x)
    jsonlite::write_json(
      o,
      path = glue::glue("{tools::file_path_sans_ext(x)}.json")
    )
  })
dir.create("json")
list.files(pattern = "json") %>%
  walk(function(x){
    file.copy(x, glue::glue("json/{x}"))
    unlink(x)
  })
```

