---
title: "Wikileaks Twitter DM - Timeline"
author: '@_colinfay'
date: "`r Sys.Date()`"
fig_width: 10
fig_height: 4 
navlink: "[Wikileaks Twitter DM](https://colinfay.me/wikileaksdm)"
og:
  type: "article"
  title: "Wikileaks Twitter DM"
footer:
  - content: '<a href="https://colinfay.me">colinfay.me</a> • <a href="https://twitter.com/_ColinFay">@_colinfay</a><br/>'
output: markdowntemplates::skeleton
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("funs.R")
```

`r shiny::includeMarkdown("intro.Rmd")`

## Count of daily DMs

A dataset with 2 columns 

+ date: the date
+ n: number of DMs 

#### `r fa("download")` [daily.csv](daily.csv)

```{r}
read_csv("daily.csv") %>%
  dt()
```

```{r}
full <- read_csv("wikileaks_dm.csv") 
dg(full, main = "DMs by day, 2015-2017", col = 1)
```

<details>
<summary>Static plot</summary>
```{r fig.width=10, fig.height=6}
ggcount(full, main = "Wikileaks Twitter DM - DMs by day, 2015-2017", col = 1) 
```
</details>

## DMs by year {.tabset}

3 datasets (1 per year), each with 3 columns: 

+ text: extracted text 
+ date: date of the dm
+ user: user who sent the dm

### 2015

#### `r fa("download")` [2015.csv](2015.csv)

```{r}
quinze <- read_csv("2015.csv") 
quinze %>% 
  dt()
```

```{r}
dg(quinze, main = "DMs by day, 2015", col = 2)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount(quinze, main = "Wikileaks Twitter DM - DMs by day, 2015", col = 2)
```

</details>

### 2016

#### `r fa("download")` [2016.csv](2016.csv)

```{r}
seize <- read_csv("2016.csv")
seize %>% 
  dt()
```

```{r}
dg(seize, main = "DMs by day, 2016", col = 3)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount(seize, main = "Wikileaks Twitter DM - DMs by day, 2016", col = 3)
```

</details>

### 2017

#### `r fa("download")` [2017.csv](2017.csv)

```{r}
dixsept <- read_csv("2017.csv") 
dixsept %>% 
  dt()
```


```{r}
dg(dixsept, main = "DMs by day, 2017", col = 4)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount(dixsept, main = "Wikileaks Twitter DM - DMs by day, 2017", col = 4)

```

</details>

`r shiny::includeMarkdown("outro.Rmd")`