---
title: "Wikileaks Twitter DM - Users"
author: '@_colinfay'
date: "`r Sys.Date()`"
fig_width: 10
fig_height: 4 
navlink: "[Wikileaks Twitter DM](https://colinfay.me/wikileaksdm)"
og:
  type: "article"
  title: "Wikileaks Twitter DM"
footer:
  - content: '<a href="https://colinfay.me">colinfay.me</a> • <a href="https://twitter.com/_ColinFay">@_colinfay</a><br/>'
output: markdowntemplates::skeleton
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("funs.R")
```

`r shiny::includeMarkdown("intro.Rmd")`

## Monthly participation by user

```{r}
full <- read_csv("wikileaks_dm.csv") 
library(lubridate)
r <- full %>%
  mutate(date = floor_date(date, "month")) %>% 
  count(date, user) %>% 
  spread(user, n) %>%
  as.data.frame()
rownames(r) <- r$date
dygraph(r, main = "Monthly participation by user", width = "100%") %>%
    dyRangeSelector(height = 40)
```

<details>
<summary>Static plot</summary>
```{r fig.width=10, fig.height=6}
full %>%
  mutate(date = floor_date(date, "month")) %>%
  count(date, user) %>% 
  ggplot() + 
  aes(date, n, group = user, color = user) +
  scale_color_manual(values = colours) +
   geom_line() + 
      labs(
      title = "Monthly participation by user",
      subtitle = "Data via Emma Best - https://emma.best",
      x = "Date",
      y = "Number of DMs"
    ) + th()
```
</details>

## Count of user participation

A dataset with 2 columns 

+ user: the user
+ n: number of DMs in the corpus for that user

#### `r fa("download")` [user_count.csv](user_count.csv)

```{r}
read_csv("user_count.csv") %>% 
  dt()
```

```{r fig.width=10, fig.height=6}
read_csv("user_count.csv") %>% 
  ggplot() + 
  aes(reorder(user, n), n) +
  geom_col(fill=colours[5]) +
  coord_flip() +
    labs(
      title = "User participation",
      subtitle = "Data via Emma Best - https://emma.best",
      x = " ",
      y = "Number of DMs"
    ) + 
    th()
```

### DMs by users

15 datasets (1/user), each with 3 columns: 

+ text: extracted text 
+ date: date of the dm
+ user: user who sent the dm

### Bean

#### `r fa("download")` [user_Bean.csv](user_Bean.csv)

```{r}
fdt("Bean")
fdg("Bean", col = 1)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("Bean", col = 1)
```

</details>

### Cabledrum

#### `r fa("download")` [user_Cabledrum.csv](user_Cabledrum.csv)

```{r}
fdt("Cabledrum")
fdg("Cabledrum", col = 2)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("Cabledrum", col = 2)
```

</details>

### DMConversationEntry

#### `r fa("download")` [user_DMConversationEntry.csv](user_DMConversationEntry.csv)

```{r}
fdt("DMConversationEntry")
fdg("DMConversationEntry", col = 3)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("DMConversationEntry", col = 3)
```

</details>

### Emmy B

#### `r fa("download")` [user_Emmy.B.csv](user_Emmy.B.csv)

```{r}
fdt("Emmy.B")
fdg("Emmy.B", col = 4)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("Emmy.B", col = 4)
```

</details>

### LibertarianLibrarian

#### `r fa("download")` [user_LibertarianLibrarian.csv](user_LibertarianLibrarian.csv)

```{r}
fdt("LibertarianLibrarian")
fdg("LibertarianLibrarian", col = 5)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("LibertarianLibrarian", col = 5)
```

</details>

### M

#### `r fa("download")` [user_M.csv](user_M.csv)

```{r}
fdt("M")
fdg("M", col = 6)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("M", col = 6)
```

</details>

### Matt Watt

#### `r fa("download")` [user_Matt.Watt.csv](user_Matt.Watt.csv)

```{r}
fdt("Matt.Watt")
fdg("Matt.Watt", col = 7)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("Matt.Watt", col = 7)
```

</details>

### noll

#### `r fa("download")` [user_noll.csv](user_noll.csv)

```{r}
fdt("noll")
fdg("noll", col = 8)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("noll", col = 8)
```

</details>

### SAWC Sydney

#### `r fa("download")` [user_SAWC.Sydney.csv](user_SAWC.Sydney.csv)

```{r}
fdt("SAWC.Sydney")
fdg("SAWC.Sydney", col = 8)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("SAWC.Sydney", col = 8)
```

</details>

### voidiss

#### `r fa("download")` [user_voidiss.csv](user_voidiss.csv)

```{r}
fdt("voidiss")
fdg("voidiss", col = 9)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("voidiss", col = 9)
```

</details>

### WikiLeaks Press

#### `r fa("download")` [user_WikiLeaks.Press.csv](user_WikiLeaks.Press.csv)

```{r}
fdt("WikiLeaks.Press")
fdg("WikiLeaks.Press", col = 10)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("WikiLeaks.Press", col = 10)
```

</details>

### WikiLeaks Task Force

#### `r fa("download")` [user_WikiLeaks.Task.Force.csv](user_WikiLeaks.Task.Force.csv)

```{r}
fdt("WikiLeaks.Task.Force")
fdg("WikiLeaks.Task.Force", col = 11)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("WikiLeaks.Task.Force", col = 11)
```

</details>

### WikiLeaks

#### `r fa("download")` [user_WikiLeaks.csv](user_WikiLeaks.csv)

```{r}
fdt("WikiLeaks")
fdg("WikiLeaks", col = 12)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("Bean", col = 12)
```

</details>

### WISE Up Action

#### `r fa("download")` [user_WISE.Up.Action.csv](user_WISE.Up.Action.csv)

```{r}
fdt("WISE.Up.Action")
fdg("WISE.Up.Action", col = 13)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("Bean", col = 13)
```

</details>

### WISE Up Wales

#### `r fa("download")` [user_WISE.Up.Wales.csv](user_WISE.Up.Wales.csv)

```{r}
fdt("WISE.Up.Wales")
fdg("WISE.Up.Wales", col = 14)
```

<details>
<summary>Static plot</summary>

```{r fig.width=10, fig.height=6}
ggcount_user("WISE.Up.Wales", col = 14)
```

</details>

`r shiny::includeMarkdown("outro.Rmd")`